SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2020-10-21 maintex.tex
M_* -> M for consistency

Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the local stellar mass, $M_*$, giving us the specific star formation rate (sSFR). The local stellar masses used here is the stellar mass calculated by {\sc SPFIT}'s fit to the stellar continuum within each MaNGA spaxel (spatial pixel).

\begin{equation}
{\rm sSFR} = \frac{\rm SFR}{M_*}
\end{equation}

>>>>

Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the local stellar mass, $M$, giving us the specific star formation rate (sSFR). The local stellar masses used here is the stellar mass calculated by {\sc SPFIT}'s fit to the stellar continuum within each MaNGA spaxel (spatial pixel).

\begin{equation}
{\rm sSFR} = \frac{\rm SFR}{M}
\end{equation}
